\textbf{ Spectrophotometric parallaxes with linear models:\\ Accurate distances for luminous red-giant stars }

### 2018-10-21 paper/sp.tex
table
adjusting cluster words

Another validation of the results can be obtained by looking at known
clusters or spatially compact objects in the data.
In \figurename~\ref{fig:clusters}, we show the parallax distribution from \gaia\ and
the spectrophotometric-parallax distribution from our model for stars that are
astrometrically confirmed members of known stellar clusters.
The cluster members were found by hand, looking at sky and proper-motion distributions
centered on literature values.
In each case we are plotting only very securely identified cluster members; that
is, membership is conservative.
These clusters span some range in metallicity and age, and therefore test
the accuracy of the method for different kinds of populations.
With the exception of \acronym{M71}, these figures 
indicate that both \gaia\ and the spectrophotometric parallaxes appear to be unbiased
for these clusters and the range in abundances and ages they represent.
The case of cluster \acronym{M71} is troubling, but after searching for trends with
housekeeping data (also see \figurename~\ref{fig:residuals}) we don't find any correlations
with parallax offsets.
\begin{figure}
~\hfill\includegraphics[width=0.7\textwidth]{clusters.pdf}\hfill~
\caption{The \gaia\ astrometric parallaxes $\gparallax_n$
  and spectrophotometric parallaxes $\sparallax_n$ for member stars for
  four stellar clusters in the \apogee\ observing footprint. The spectrophotometric
  parallaxes and their inverse-variance-weighted mean and the astrometric parallaxes
  and their inverse-variance-weighted mean
  are shown as vertical lines.
  Cluster members were identified to be close to the cluster in celestial coordinates
  and comoving in proper motion.\label{fig:clusters}}
\end{figure}

@@

\newpage
\begin{longrotatetable}
\startlongtable
\begin{deluxetable*}{lllllcc}
\tablecaption{HOGG and ACE TBD: The generated spectrophotometric parallaxes.
This table is just a snippet; the full table is available online (HOGG HOW?)\label{tab:output}}
\tablehead{\dcolhead{\texttt{2MASS\_ID}} & \dcolhead{\texttt{Gaia\_parallax}} & \dcolhead{\texttt{Gaia\_parallax\_err}} & \dcolhead{\texttt{spec\_parallax}} & \dcolhead{\texttt{spec\_parallax\_err}} & \dcolhead{\texttt{training\_set}} & \dcolhead{\texttt{sample}}}
\startdata
2M00000002+7417074 & 0.3191 & 0.0329 & 0.3185 & 0.0164 & 0 & B \\
2M00000317+5821383 & 0.3643 & 0.051 & 0.4428 & 0.0183 & 0 & A \\
2M00000546+6152107 & 0.3154 & 0.0351 & 0.3292 & 0.0164 & 0 & B \\
2M00000797+6436119 & 0.0771 & 0.0841 & 0.1943 & 0.0194 & 1 & B \\
2M00001719+6221324 & 0.1395 & 0.0439 & 0.1564 & 0.0128 & 0 & B \\
2M00002005+5703467 & 0.3003 & 0.0247 & 0.2372 & 0.0203 & 0 & B \\
2M00002036+6153416 & 0.0657 & 0.0637 & 0.1347 & 0.0131 & 1 & A \\
2M00002118+6136420 & 0.1936 & 0.0323 & 0.2173 & 0.0133 & 1 & B \\
2M00002227+6223341 & 0.1965 & 0.045 & 0.1461 & 0.0089 & 0 & B \\
2M00002472+5518473 & 0.0947 & 0.0207 & 0.1473 & 0.0096 & 1 & B \\
2M00002908+6140446 & 0.1675 & 0.046 & 0.1914 & 0.0176 & 1 & A \\
2M00003061+5820590 & 0.1669 & 0.0339 & 0.3502 & 0.029 & 1 & A \\
... & ... & ... & ... & ... & ... & ...  \\
 \enddata
\tablecomments{Columns show...}
\end{deluxetable*}
\end{longrotatetable}
\newpage

@@

\begin{figure}
\centering
~\hfill\includegraphics[width=0.8\textwidth]{./CMD4.pdf}\hfill~
\caption{color-magnitude-diagram.\label{fig:cmd}}
\end{figure}

ACE: ADD HERE the Color-magnitude diagrams for high snr and training set.
HOGG: Discussion here of CMD and AGB stars.

>>>>

Another validation of the results can be obtained by looking at known
clusters or spatially compact objects in the data.
In \figurename~\ref{fig:clusters}, we show the parallax distribution from \gaia\ and
the spectrophotometric-parallax distribution from our model for stars that are
astrometrically confirmed members of three of the stellar clusters in which we
validated our results.
The cluster members were found by hand, looking at sky and proper-motion distributions
centered on literature values.
In each case we are plotting only very securely identified cluster members; that
is, membership is conservative.
We chose three clusters to span some range in metallicity and age, and therefore test
the accuracy of the method for different kinds of populations.
With the exception of \acronym{M71}, the clusters we tested
indicate that both \gaia\ and the spectrophotometric parallaxes appear to be unbiased
for these clusters and the range in abundances and ages they represent.
The case of cluster \acronym{M71} is troubling, but after searching for trends with
housekeeping data (also see \figurename~\ref{fig:residuals}) we don't find any correlations
with parallax offsets.
\begin{figure}
~\hfill\includegraphics[width=0.7\textwidth]{clusters.pdf}\hfill~
\caption{The \gaia\ astrometric parallaxes $\gparallax_n$
  and spectrophotometric parallaxes $\sparallax_n$ for member stars for
  three of the stellar clusters in the \apogee\ observing footprint. The spectrophotometric
  parallaxes and their inverse-variance-weighted mean and the astrometric parallaxes
  and their inverse-variance-weighted mean
  are shown as vertical lines.
  Cluster members were identified to be close to the cluster in celestial coordinates
  and comoving in proper motion.\label{fig:clusters}}
\end{figure}

@@

\newpage
\begin{longrotatetable}
\startlongtable
\begin{deluxetable*}{ccccccc}
\tablecaption{HOGG and ACE TBD: The generated spectrophotometric parallaxes.
This table is just a snippet; the full table is available online (HOGG HOW?)\label{tab:output}}
\tablehead{\dcolhead{\texttt{2MASS\_ID}} & \dcolhead{\texttt{Gaia\_parallax}} & \dcolhead{\texttt{Gaia\_parallax\_err}} & \dcolhead{\texttt{spec\_parallax}} & \dcolhead{\texttt{spec\_parallax\_err}} & \dcolhead{\texttt{training\_set}} & \dcolhead{\texttt{sample}}}
\startdata
2M00000002+7417074 & 0.3191 & 0.0329 & 0.3185 & 0.0164 & 0 & B \\
2M00000317+5821383 & 0.3643 & 0.0510 & 0.4428 & 0.0183 & 0 & A \\
2M00000546+6152107 & 0.3154 & 0.0351 & 0.3292 & 0.0164 & 0 & B \\
2M00000797+6436119 & 0.0771 & 0.0841 & 0.1943 & 0.0194 & 1 & B \\
2M00001719+6221324 & 0.1395 & 0.0439 & 0.1564 & 0.0128 & 0 & B \\
2M00002005+5703467 & 0.3003 & 0.0247 & 0.2372 & 0.0203 & 0 & B \\
2M00002036+6153416 & 0.0657 & 0.0637 & 0.1347 & 0.0131 & 1 & A \\
2M00002118+6136420 & 0.1936 & 0.0323 & 0.2173 & 0.0133 & 1 & B \\
2M00002227+6223341 & 0.1965 & 0.0450 & 0.1461 & 0.0089 & 0 & B \\
2M00002472+5518473 & 0.0947 & 0.0207 & 0.1473 & 0.0096 & 1 & B \\
2M00002908+6140446 & 0.1675 & 0.0460 & 0.1914 & 0.0176 & 1 & A \\
2M00003061+5820590 & 0.1669 & 0.0339 & 0.3502 & 0.0290 & 1 & A \\
... & ... & ... & ... & ... & ... & ...  \\
 \enddata
\tablecomments{Columns show...}
\end{deluxetable*}
\end{longrotatetable}
\newpage

@@

HOGG: Discussion here of CMD and AGB stars.
\begin{figure}
\centering
~\hfill\includegraphics[width=0.8\textwidth]{./CMD4.pdf}\hfill~
\caption{HOGG color-magnitude-diagram.\label{fig:cmd}}
\end{figure}
